PPM-S

### 2021-08-11 index.Rmd
unir estudios & pendientes

---
title: "PPM-S"
csl: "input/bib/apa6.csl"
bibliography: "input/bib/zlibrary.bib"
author: " "
output:
    bookdown::html_document2:
            smart: false
            number_sections: false
---

>>>>

---
title: "PPM-S"
csl: "input/bib/apa6.csl"
bibliography: "input/bib/meritocracy.bib"
author: " "
output:
    bookdown::html_document2:
            smart: false
            number_sections: false
---
